A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
final ??

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} and is converted to a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}, which will be used to sample $\Omega_x$ in the path tracing algorithm. To each node $n$ of the skeleton, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ is the direction to follow in order to find a light source.

@@

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$. An example is shown on Fig.~\ref{fig::example_imp}.

\begin{figure}[tb]
\begin{center}
\begin{tabular}{c|c}
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} &
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} \\
\end{tabular}
\caption[Example of importance point construction]{\label{fig::example_imp} \textbf{On the left}, we illustrate the importance point $imp_n$ associated to a node $n$. The dotted black line shows the closest node to $n$ not included in $V_n$. \textbf{On the right}, an example of the curvilinear skeleton (in red) obtained in the Sponza scene.}
\end{center}
\end{figure}

@@

\begin{figure}[tb]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & fig.\ref{fig:redcorridor} & fig.\ref{fig:examples} far left & fig.\ref{fig:examples} far right \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Time to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right is for our method}
\label{tab:timing}
\end{figure}

>>>>

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} (as shown on Fig.~\ref{fig::example_imp} on the right) and is converted to a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}, which will be used to sample $\Omega_x$ in the path tracing algorithm. To each node $n$ of the skeleton, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ is the direction to follow in order to find a light source.

@@

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$. An example is shown on Fig.~\ref{fig::example_imp} on the left.

\begin{figure}[tb]
\begin{center}
\begin{tabular}{l|r}
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} ~~~~~~&
	~~~~~~ \myincludegraphics{0.6\textwidth}{skel.jpg} \\
\end{tabular}
\caption[Example of importance point construction]{\label{fig::example_imp} \textbf{On the left}, we illustrate the importance point $imp_n$ associated to a node $n$. The dotted black line shows the closest node to $n$ not included in $V_n$. \textbf{On the right}, an example of the curvilinear skeleton (in red) obtained in the Sponza scene.}
\end{center}
\end{figure}

@@

\begin{figure}[tb]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & Corridor & Sponza 1 & Sponza 2 (Fig. \ref{fig:results}) \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Time to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right is for our method}
\label{tab:timing}
\end{figure}
